First Project On Reproducible Reaserch
======================================

Loading the activity.csv file

```{r echo = TRUE}
library(tidyverse)
activity <- read.csv("activity.csv", header = TRUE, sep = ",")
summary(activity)

```

calculating the total no of steps taken per day and plotting them using histogram

```{r echo = TRUE}
activity_byDay <- activity %>% 
                       group_by(date)%>%
                       summarise(total_steps = sum(steps))

activity_byDay$date <- as.Date(activity_byDay$date)
ggplot(activity_byDay, aes(x = date, y = total_steps)) +
        geom_histogram(stat = "identity")
```

claculating the mean and median off total no of steps taken per day

```{r echo = TRUE}
mean(activity_byDay$total_steps, na.rm = TRUE)

median(activity_byDay$total_steps, na.rm = TRUE)

```

```{r echo = TRUE}
activity_mean <- activity %>%
        group_by(interval) %>%
        summarise(mean_steps = mean(steps, na.rm = TRUE))
```

average steps over time series plot

```{r echo = TRUE}
ggplot(activity_mean, aes(x = interval, y = mean_steps)) +
        geom_line()
```
calculating no of rows containing in activity data
```{r echo = TRUE}
sum(is.na(activity))
```
imputing the na vlaues using mean_steps fill in the na containing rows
```{r echo = TRUE}
for(i in 1:nrow(activity)){
        if(is.na(activity$steps[i])){
                activity$steps[i] = activity_mean$mean_steps[which(activity_mean$interval == activity$interval[i])]
        }
}
sum(is.na(activity$steps))
```
after imputing ploting the histogram of total no of steps per day
```{r echo = TRUE}
activity$date = as.Date(activity$date)
ggplot(activity, aes(x = date, y = steps))+
        geom_histogram(stat = "identity")
```
mean and median of the total no of steps per day(after imputing)
```{r echo = TRUE}
newActivity_byDay <- activity %>% 
                       group_by(date)%>%
                       summarise(total_steps = sum(steps))

mean(newActivity_byDay$total_steps)
median(newActivity_byDay$total_steps)
```
creating new variable containing weekday and weekend
```{r echo = TRUE}
activity <- activity %>% mutate(typeofDay = ifelse(weekdays(activity$date) == "Saturday" | weekdays(activity$date) == "Sunday", "weekend", "weekday"))
table(activity$typeofDay)
```

```{r echo = TRUE}
newActivity_mean <- activity %>%
        group_by(interval, typeofDay) %>%
        summarise(mean_steps = mean(steps, na.rm = TRUE))
```
ploting the avg no of steps taken per each day using panels weekday and weekend
```{r echo = TRUE}
ggplot(newActivity_mean, aes(x = interval, y = mean_steps)) +
        geom_line() +
        facet_grid(typeofDay~.)
```








